Packaging research artefacts with RO-Crate

### 2022-01-02 latex/ro-crate-proof.tex
ro-crate-proof separate

%b23 ###bbsrt2
%b13 ###
\bibitem{doi:10.5281/zenodo.3250687}
%
\begin{barticle}
\bauthor{\binits{E.\'{O}.}~\bsnm{Carrag\'{a}in}},
\bauthor{\binits{C.}~\bsnm{Goble}},
\bauthor{\binits{P.}~\bsnm{Sefton}} and
\bauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\batitle{A lightweight approach to research object data packaging},
\bjtitle{Zenodo}
(\byear{2019}).
\bid{doi={10.5281/zenodo.3250687}}
\end{barticle}
%
\OrigBibText
E.{\'{O}}.~Carrag\'{a}in,
C.~Goble,
P.~Sefton and
S.~Soiland-Reyes,
\textit{A lightweight approach to research object data packaging},
Zenodo
(2019).
doi:10.5281/zenodo.3250687.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b103 ###bbsrt2
%b39 ###
\bibitem{doi:10.5281/zenodo.1445817}
%
\begin{bchapter}
\bauthor{\binits{P.}~\bsnm{Sefton}},
in: \bbtitle{Datacrate Submisssion to the Workshop on Research Objects},
\bconflocation{Zenodo},
\byear{2018}.
\bid{doi={10.5281/zenodo.1445817}}
\end{bchapter}
%
\OrigBibText
P.~Sefton,
\textit{Datacrate Submisssion To The Workshop On Research Objects},
Zenodo
(2018).
doi:10.5281/zenodo.1445817.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b105 ###bbsrt2
%b62 ###
\bibitem{doi:10.5281/zenodo.3541888}
%
\begin{botherref}
\oauthor{\binits{P.}~\bsnm{Sefton}},
\oauthor{\binits{E.\'{O}.}~\bsnm{Carrag\'{a}in}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{O.}~\bsnm{Corcho}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{R.}~\bsnm{Palma}},
\oauthor{\binits{F.}~\bsnm{Coppens}},
\oauthor{\binits{C.}~\bsnm{Goble}},
\oauthor{\binits{J.M.}~\bsnm{Fern\'{a}ndez}},
\oauthor{\binits{K.}~\bsnm{Chard}},
\oauthor{\binits{J.M.}~\bsnm{Gomez-Perez}},
\oauthor{\binits{M.R.}~\bsnm{Crusoe}},
\oauthor{\binits{I.}~\bsnm{Eguinoa}},
\oauthor{\binits{N.}~\bsnm{Juty}},
\oauthor{\binits{K.}~\bsnm{Holmes}},
\oauthor{\binits{J.A.}~\bsnm{Clark}},
\oauthor{\binits{S.}~\bsnm{Capella-Gutierrez}},
\oauthor{\binits{A.J.G.}~\bsnm{Gray}},
\oauthor{\binits{S.}~\bsnm{Owen}},
\oauthor{\binits{A.R.}~\bsnm{Williams}},
\oauthor{\binits{G.}~\bsnm{Tartari}},
\oauthor{\binits{F.}~\bsnm{Bacall}} and
\oauthor{\binits{T.}~\bsnm{Thelen}},
{RO}-Crate Metadata Specification 1.0,
2019.
\bid{doi={10.5281/zenodo.3541888}}
\end{botherref}
%
\OrigBibText
P.~Sefton,
E.{\'{O}}.~Carrag\'{a}in,
S.~Soiland-Reyes,
O.~Corcho,
D.~Garijo,
R.~Palma,
F.~Coppens,
C.~Goble,
J.M.~Fern\'{a}ndez,
K.~Chard,
J.M.~Gomez-Perez,
M.R.~Crusoe,
I.~Eguinoa,
N.~Juty,
K.~Holmes,
J.A.~Clark,
S.~Capella-Gutierrez,
A.J.G.~Gray,
S.~Owen,
A.R.~Williams,
G.~Tartari,
F.~Bacall and
T.~Thelen,
{RO}-Crate Metadata Specification 1.0,
2019.
doi:10.5281/zenodo.3541888.
\url{https://w3id.org/ro/crate/1.0}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

%b106 ###bbsrt2
%b33 ###
\bibitem{doi:10.5281/zenodo.4541002}
%
\begin{botherref}
\oauthor{\binits{P.}~\bsnm{Sefton}},
\oauthor{\binits{E.\'{O}.}~\bsnm{Carrag\'{a}in}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{O.}~\bsnm{Corcho}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{R.}~\bsnm{Palma}},
\oauthor{\binits{F.}~\bsnm{Coppens}},
\oauthor{\binits{C.}~\bsnm{Goble}},
\oauthor{\binits{J.M.}~\bsnm{Fern\'{a}ndez}},
\oauthor{\binits{K.}~\bsnm{Chard}},
\oauthor{\binits{J.M.}~\bsnm{Gomez-Perez}},
\oauthor{\binits{M.R.}~\bsnm{Crusoe}},
\oauthor{\binits{I.}~\bsnm{Eguinoa}},
\oauthor{\binits{N.}~\bsnm{Juty}},
\oauthor{\binits{K.}~\bsnm{Holmes}},
\oauthor{\binits{J.A.}~\bsnm{Clark}},
\oauthor{\binits{S.}~\bsnm{Capella-Gutierrez}},
\oauthor{\binits{A.J.G.}~\bsnm{Gray}},
\oauthor{\binits{S.}~\bsnm{Owen}},
\oauthor{\binits{A.R.}~\bsnm{Williams}},
\oauthor{\binits{G.}~\bsnm{Tartari}},
\oauthor{\binits{F.}~\bsnm{Bacall}},
\oauthor{\binits{T.}~\bsnm{Thelen}},
\oauthor{\binits{H.}~\bsnm{M\'{e}nager}},
\oauthor{\binits{L.R.-N.}~\bsnm{Navas}},
\oauthor{\binits{P.}~\bsnm{Walk}},
\oauthor{\binits{B.}~\bsnm{Whitehead}},
\oauthor{\binits{M.}~\bsnm{Wilkinson}},
\oauthor{\binits{P.}~\bsnm{Groth}},
\oauthor{\binits{E.}~\bsnm{Bremer}},
\oauthor{\binits{L.G.}~\bsnm{Castro}},
\oauthor{\binits{K.}~\bsnm{Sebby}},
\oauthor{\binits{A.}~\bsnm{Kanitz}},
\oauthor{\binits{A.}~\bsnm{Trisovic}},
\oauthor{\binits{G.}~\bsnm{Kennedy}},
\oauthor{\binits{M.}~\bsnm{Graves}},
\oauthor{\binits{J.}~\bsnm{Koehorst}},
\oauthor{\binits{S.}~\bsnm{Leo}} and
\oauthor{\binits{M.}~\bsnm{Portier}},
{RO}-Crate Metadata Specification 1.1.1,
2021.
\bid{doi={10.5281/zenodo.4541002}}
\end{botherref}
%
\OrigBibText
P.~Sefton,
E.{\'{O}}.~Carrag\'{a}in,
S.~Soiland-Reyes,
O.~Corcho,
D.~Garijo,
R.~Palma,
F.~Coppens,
C.~Goble,
J.M.~Fern\'{a}ndez,
K.~Chard,
J.M.~Gomez-Perez,
M.R.~Crusoe,
I.~Eguinoa,
N.~Juty,
K.~Holmes,
J.A.~Clark,
S.~Capella-Gutierrez,
A.J.G.~Gray,
S.~Owen,
A.R.~Williams,
G.~Tartari,
F.~Bacall,
T.~Thelen,
H.~M\'{e}nager,
L.R.-N.~Navas,
P.~Walk,
B.~Whitehead,
M.~Wilkinson,
P.~Groth,
E.~Bremer,
L.G.~Castro,
K.~Sebby,
A.~Kanitz,
A.~Trisovic,
G.~Kennedy,
M.~Graves,
J.~Koehorst,
S.~Leo and
M.~Portier,
{RO}-Crate Metadata Specification 1.1.1,
2021.
doi:10.5281/zenodo.4541002.
\url{https://w3id.org/ro/crate/1.1}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

%b107 ###bbsrt2
%b63 ###
\bibitem{doi:10.5281/zenodo.4031327}
%
\begin{botherref}
\oauthor{\binits{P.}~\bsnm{Sefton}},
\oauthor{\binits{E.\'{O}.}~\bsnm{Carrag\'{a}in}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{O.}~\bsnm{Corcho}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{R.}~\bsnm{Palma}},
\oauthor{\binits{F.}~\bsnm{Coppens}},
\oauthor{\binits{C.}~\bsnm{Goble}},
\oauthor{\binits{J.M.}~\bsnm{Fern\'{a}ndez}},
\oauthor{\binits{K.}~\bsnm{Chard}},
\oauthor{\binits{J.M.}~\bsnm{Gomez-Perez}},
\oauthor{\binits{M.R.}~\bsnm{Crusoe}},
\oauthor{\binits{I.}~\bsnm{Eguinoa}},
\oauthor{\binits{N.}~\bsnm{Juty}},
\oauthor{\binits{K.}~\bsnm{Holmes}},
\oauthor{\binits{J.A.}~\bsnm{Clark}},
\oauthor{\binits{S.}~\bsnm{Capella-Gutierrez}},
\oauthor{\binits{A.J.G.}~\bsnm{Gray}},
\oauthor{\binits{S.}~\bsnm{Owen}},
\oauthor{\binits{A.R.}~\bsnm{Williams}},
\oauthor{\binits{G.}~\bsnm{Tartari}},
\oauthor{\binits{F.}~\bsnm{Bacall}},
\oauthor{\binits{T.}~\bsnm{Thelen}},
\oauthor{\binits{H.}~\bsnm{M\'{e}nager}},
\oauthor{\binits{L.}~\bsnm{Rodr\'{\i}guez-Navas}},
\oauthor{\binits{P.}~\bsnm{Walk}},
\oauthor{\binits{B.}~\bsnm{Whitehead}},
\oauthor{\binits{M.}~\bsnm{Wilkinson}},
\oauthor{\binits{P.}~\bsnm{Groth}},
\oauthor{\binits{E.}~\bsnm{Bremer}},
\oauthor{\binits{L.G.}~\bsnm{Castro}},
\oauthor{\binits{K.}~\bsnm{Sebby}},
\oauthor{\binits{A.}~\bsnm{Kanitz}},
\oauthor{\binits{A.}~\bsnm{Trisovic}},
\oauthor{\binits{G.}~\bsnm{Kennedy}},
\oauthor{\binits{M.}~\bsnm{Graves}},
\oauthor{\binits{J.}~\bsnm{Koehorst}} and
\oauthor{\binits{S.}~\bsnm{Leo}},
{RO}-Crate Metadata Specification 1.1,
2020.
\bid{doi={10.5281/zenodo.4031327}}
\end{botherref}
%
\OrigBibText
P.~Sefton,
E.{\'{O}}.~Carrag\'{a}in,
S.~Soiland-Reyes,
O.~Corcho,
D.~Garijo,
R.~Palma,
F.~Coppens,
C.~Goble,
J.M.~Fern\'{a}ndez,
K.~Chard,
J.M.~Gomez-Perez,
M.R.~Crusoe,
I.~Eguinoa,
N.~Juty,
K.~Holmes,
J.A.~Clark,
S.~Capella-Gutierrez,
A.J.G.~Gray,
S.~Owen,
A.R.~Williams,
G.~Tartari,
F.~Bacall,
T.~Thelen,
H.~M\'{e}nager,
L.~Rodr\'iguez-Navas,
P.~Walk,
B.~Whitehead,
M.~Wilkinson,
P.~Groth,
E.~Bremer,
L.G.~Castro,
K.~Sebby,
A.~Kanitz,
A.~Trisovic,
G.~Kennedy,
M.~Graves,
J.~Koehorst and
S.~Leo,
{RO}-Crate Metadata Specification 1.1,
2020.
doi:10.5281/zenodo.4031327.
\url{https://w3id.org/ro/crate/1.1}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

>>>>

%b23 ###bbsrt2
%b13 ###
\bibitem{doi:10.5281/zenodo.3250687}
%
\begin{bchapter}
\bauthor{\binits{E.}~\bsnm{\'{O}~Carrag\'{a}in}},
\bauthor{\binits{C.}~\bsnm{Goble}},
\bauthor{\binits{P.}~\bsnm{Sefton}} and
\bauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\bctitle{A lightweight approach to research object data packaging}.
in: \bbtitle{Bioinformatics Open Source Conference (BOSC2019)}, 
2019-07-24/2019-07-25, 
\blocation{Basel, Switzerland}.
\bpublisher{Zenodo}
(\byear{2019}).
\bid{doi={10.5281/zenodo.3250687}}
\end{bchapter}
%
\OrigBibText
E.{\'{O}}.~Carrag\'{a}in,
C.~Goble,
P.~Sefton and
S.~Soiland-Reyes,
\textit{A lightweight approach to research object data packaging},
Zenodo
(2019).
doi:10.5281/zenodo.3250687.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b103 ###bbsrt2
%b39 ###
\bibitem{doi:10.5281/zenodo.1445817}
%
\begin{bchapter}
\bauthor{\binits{P.}~\bsnm{Sefton}},
\bauthor{\binits{G.}~\bsnm{Devine}},
\bauthor{\binits{C.}~\bsnm{Evenhuis}},
\bauthor{\binits{M.}~\bsnm{Lynch}},
\bauthor{\binits{S.}~\bsnm{Wise}},
\bauthor{\binits{M.}~\bsnm{Lake}} and
\bauthor{\binits{D.}~\bsnm{Loxton}}: 
\bctitle{DataCrate: a method of packaging, distributing, displaying and archiving Research Objects}.
in: \bbtitle{Workshop on Research Objects (RO 2018)},
29 Oct \byear{2018} at
IEEE eScience 2018,
\bconflocation{Amsterdam, Netherland}.
\bpublisher{Zenodo}
\bid{doi={10.5281/zenodo.1445817}}
\end{bchapter}
%
\OrigBibText
P.~Sefton,
\textit{Datacrate Submisssion To The Workshop On Research Objects},
Zenodo
(2018).
doi:10.5281/zenodo.1445817.
\endOrigBibText
\bptok{structpyb}
\endbibitem

@@

%b105 ###bbsrt2
%b62 ###
\bibitem{doi:10.5281/zenodo.3541888}
%
\begin{botherref}
\oauthor{\binits{P.}~\bsnm{Sefton}},
\oauthor{\binits{E.}~\bsnm{\'{O}~Carrag\'{a}in}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{O.}~\bsnm{Corcho}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{R.}~\bsnm{Palma}},
\oauthor{\binits{F.}~\bsnm{Coppens}},
\oauthor{\binits{C.}~\bsnm{Goble}},
\oauthor{\binits{J.M.}~\bsnm{Fern\'{a}ndez}},
\oauthor{\binits{K.}~\bsnm{Chard}},
\oauthor{\binits{J.M.}~\bsnm{Gomez-Perez}},
\oauthor{\binits{M.R.}~\bsnm{Crusoe}},
\oauthor{\binits{I.}~\bsnm{Eguinoa}},
\oauthor{\binits{N.}~\bsnm{Juty}},
\oauthor{\binits{K.}~\bsnm{Holmes}},
\oauthor{\binits{J.A.}~\bsnm{Clark}},
\oauthor{\binits{S.}~\bsnm{Capella-Gutierrez}},
\oauthor{\binits{A.J.G.}~\bsnm{Gray}},
\oauthor{\binits{S.}~\bsnm{Owen}},
\oauthor{\binits{A.R.}~\bsnm{Williams}},
\oauthor{\binits{G.}~\bsnm{Tartari}},
\oauthor{\binits{F.}~\bsnm{Bacall}} and
\oauthor{\binits{T.}~\bsnm{Thelen}},
{RO}-Crate Metadata Specification 1.0,
2019.
\bid{doi={10.5281/zenodo.3541888}}
\end{botherref}
%
\OrigBibText
P.~Sefton,
E.{\'{O}}.~Carrag\'{a}in,
S.~Soiland-Reyes,
O.~Corcho,
D.~Garijo,
R.~Palma,
F.~Coppens,
C.~Goble,
J.M.~Fern\'{a}ndez,
K.~Chard,
J.M.~Gomez-Perez,
M.R.~Crusoe,
I.~Eguinoa,
N.~Juty,
K.~Holmes,
J.A.~Clark,
S.~Capella-Gutierrez,
A.J.G.~Gray,
S.~Owen,
A.R.~Williams,
G.~Tartari,
F.~Bacall and
T.~Thelen,
{RO}-Crate Metadata Specification 1.0,
2019.
doi:10.5281/zenodo.3541888.
\url{https://w3id.org/ro/crate/1.0}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

%b106 ###bbsrt2
%b33 ###
\bibitem{doi:10.5281/zenodo.4541002}
%
\begin{botherref}
\oauthor{\binits{P.}~\bsnm{Sefton}},
\oauthor{\binits{E.}~\bsnm{\'{O}~Carrag\'{a}in}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{O.}~\bsnm{Corcho}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{R.}~\bsnm{Palma}},
\oauthor{\binits{F.}~\bsnm{Coppens}},
\oauthor{\binits{C.}~\bsnm{Goble}},
\oauthor{\binits{J.M.}~\bsnm{Fern\'{a}ndez}},
\oauthor{\binits{K.}~\bsnm{Chard}},
\oauthor{\binits{J.M.}~\bsnm{Gomez-Perez}},
\oauthor{\binits{M.R.}~\bsnm{Crusoe}},
\oauthor{\binits{I.}~\bsnm{Eguinoa}},
\oauthor{\binits{N.}~\bsnm{Juty}},
\oauthor{\binits{K.}~\bsnm{Holmes}},
\oauthor{\binits{J.A.}~\bsnm{Clark}},
\oauthor{\binits{S.}~\bsnm{Capella-Gutierrez}},
\oauthor{\binits{A.J.G.}~\bsnm{Gray}},
\oauthor{\binits{S.}~\bsnm{Owen}},
\oauthor{\binits{A.R.}~\bsnm{Williams}},
\oauthor{\binits{G.}~\bsnm{Tartari}},
\oauthor{\binits{F.}~\bsnm{Bacall}},
\oauthor{\binits{T.}~\bsnm{Thelen}},
\oauthor{\binits{H.}~\bsnm{M\'{e}nager}},
\oauthor{\binits{L.R.-N.}~\bsnm{Navas}},
\oauthor{\binits{P.}~\bsnm{Walk}},
\oauthor{\binits{B.}~\bsnm{Whitehead}},
\oauthor{\binits{M.}~\bsnm{Wilkinson}},
\oauthor{\binits{P.}~\bsnm{Groth}},
\oauthor{\binits{E.}~\bsnm{Bremer}},
\oauthor{\binits{L.G.}~\bsnm{Castro}},
\oauthor{\binits{K.}~\bsnm{Sebby}},
\oauthor{\binits{A.}~\bsnm{Kanitz}},
\oauthor{\binits{A.}~\bsnm{Trisovic}},
\oauthor{\binits{G.}~\bsnm{Kennedy}},
\oauthor{\binits{M.}~\bsnm{Graves}},
\oauthor{\binits{J.}~\bsnm{Koehorst}},
\oauthor{\binits{S.}~\bsnm{Leo}} and
\oauthor{\binits{M.}~\bsnm{Portier}},
{RO}-Crate Metadata Specification 1.1.1,
2021.
\bid{doi={10.5281/zenodo.4541002}}
\end{botherref}
%
\OrigBibText
P.~Sefton,
E.{\'{O}}.~Carrag\'{a}in,
S.~Soiland-Reyes,
O.~Corcho,
D.~Garijo,
R.~Palma,
F.~Coppens,
C.~Goble,
J.M.~Fern\'{a}ndez,
K.~Chard,
J.M.~Gomez-Perez,
M.R.~Crusoe,
I.~Eguinoa,
N.~Juty,
K.~Holmes,
J.A.~Clark,
S.~Capella-Gutierrez,
A.J.G.~Gray,
S.~Owen,
A.R.~Williams,
G.~Tartari,
F.~Bacall,
T.~Thelen,
H.~M\'{e}nager,
L.R.-N.~Navas,
P.~Walk,
B.~Whitehead,
M.~Wilkinson,
P.~Groth,
E.~Bremer,
L.G.~Castro,
K.~Sebby,
A.~Kanitz,
A.~Trisovic,
G.~Kennedy,
M.~Graves,
J.~Koehorst,
S.~Leo and
M.~Portier,
{RO}-Crate Metadata Specification 1.1.1,
2021.
doi:10.5281/zenodo.4541002.
\url{https://w3id.org/ro/crate/1.1}.
\endOrigBibText
\bptok{structpyb}
\endbibitem

%b107 ###bbsrt2
%b63 ###
\bibitem{doi:10.5281/zenodo.4031327}
%
\begin{botherref}
\oauthor{\binits{P.}~\bsnm{Sefton}},
\oauthor{\binits{E.}~\bsnm{\'{O}~Carrag\'{a}in}},
\oauthor{\binits{S.}~\bsnm{Soiland-Reyes}},
\oauthor{\binits{O.}~\bsnm{Corcho}},
\oauthor{\binits{D.}~\bsnm{Garijo}},
\oauthor{\binits{R.}~\bsnm{Palma}},
\oauthor{\binits{F.}~\bsnm{Coppens}},
\oauthor{\binits{C.}~\bsnm{Goble}},
\oauthor{\binits{J.M.}~\bsnm{Fern\'{a}ndez}},
\oauthor{\binits{K.}~\bsnm{Chard}},
\oauthor{\binits{J.M.}~\bsnm{Gomez-Perez}},
\oauthor{\binits{M.R.}~\bsnm{Crusoe}},
\oauthor{\binits{I.}~\bsnm{Eguinoa}},
\oauthor{\binits{N.}~\bsnm{Juty}},
\oauthor{\binits{K.}~\bsnm{Holmes}},
\oauthor{\binits{J.A.}~\bsnm{Clark}},
\oauthor{\binits{S.}~\bsnm{Capella-Gutierrez}},
\oauthor{\binits{A.J.G.}~\bsnm{Gray}},
\oauthor{\binits{S.}~\bsnm{Owen}},
\oauthor{\binits{A.R.}~\bsnm{Williams}},
\oauthor{\binits{G.}~\bsnm{Tartari}},
\oauthor{\binits{F.}~\bsnm{Bacall}},
\oauthor{\binits{T.}~\bsnm{Thelen}},
\oauthor{\binits{H.}~\bsnm{M\'{e}nager}},
\oauthor{\binits{L.}~\bsnm{Rodr\'{\i}guez-Navas}},
\oauthor{\binits{P.}~\bsnm{Walk}},
\oauthor{\binits{B.}~\bsnm{Whitehead}},
\oauthor{\binits{M.}~\bsnm{Wilkinson}},
\oauthor{\binits{P.}~\bsnm{Groth}},
\oauthor{\binits{E.}~\bsnm{Bremer}},
\oauthor{\binits{L.G.}~\bsnm{Castro}},
\oauthor{\binits{K.}~\bsnm{Sebby}},
\oauthor{\binits{A.}~\bsnm{Kanitz}},
\oauthor{\binits{A.}~\bsnm{Trisovic}},
\oauthor{\binits{G.}~\bsnm{Kennedy}},
\oauthor{\binits{M.}~\bsnm{Graves}},
\oauthor{\binits{J.}~\bsnm{Koehorst}} and
\oauthor{\binits{S.}~\bsnm{Leo}},
{RO}-Crate Metadata Specification 1.1,
2020.
\bid{doi={10.5281/zenodo.4031327}}
\end{botherref}
%
\OrigBibText
P.~Sefton,
E.{\'{O}}.~Carrag\'{a}in,
S.~Soiland-Reyes,
O.~Corcho,
D.~Garijo,
R.~Palma,
F.~Coppens,
C.~Goble,
J.M.~Fern\'{a}ndez,
K.~Chard,
J.M.~Gomez-Perez,
M.R.~Crusoe,
I.~Eguinoa,
N.~Juty,
K.~Holmes,
J.A.~Clark,
S.~Capella-Gutierrez,
A.J.G.~Gray,
S.~Owen,
A.R.~Williams,
G.~Tartari,
F.~Bacall,
T.~Thelen,
H.~M\'{e}nager,
L.~Rodr\'iguez-Navas,
P.~Walk,
B.~Whitehead,
M.~Wilkinson,
P.~Groth,
E.~Bremer,
L.G.~Castro,
K.~Sebby,
A.~Kanitz,
A.~Trisovic,
G.~Kennedy,
M.~Graves,
J.~Koehorst and
S.~Leo,
{RO}-Crate Metadata Specification 1.1,
2020.
doi:10.5281/zenodo.4031327.
\url{https://w3id.org/ro/crate/1.1}.
\endOrigBibText
\bptok{structpyb}
\endbibitem
